---
  title: "Data Review"
author: "SLEE"
date: "10/14/2022"
output: html_document
---

```{r setup, include=FALSE}

#####Make sure you load any required packages.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
library(openxlsx)
library(readxl)
library(writexl)
library(reshape2)
library(skimr)
library(janitor)
library(lubridate)
library(ggthemes)


```

## Import Your Data

In the following code hunk, import your data.

```{r data_import}

#### Use read_csv() or another function
#### Make sure your data is converted into a tibble. 


nobel <- read.csv("nobel_final.csv")

nobel %>% 
  tibble::as.tibble() -> nobel

nobel

```

## Part 1

Using words, describe the visualization you are going to make using which variables/characteristics in your data:

*1. Histograms and density plots: distributions of winners by age.*

In the code chunk below, show your work filtering the data and create the subset of data you will display graphically.

```{r data_1}
nobel %>% 
  dplyr::select(age_get_prize) -> number_1_data


####make sure you call the data so it will display in your report

number_1_data %>% 
  ggplot2::ggplot(mapping = aes(x = age_get_prize)) +
  ggplot2::geom_histogram() +
  ggplot2::theme_minimal() -> number_1_fig

number_1_fig

```

## Part 2

Using words, describe the *second* visualization you are going to make using which variables/characteristics in your data:

*2. Bar charts: winners by Top 10 university*

In the code chunk below, show your work filtering the data and create the subset of data you will display graphically.

```{r data_2}
nobel %>% 
  dplyr::select(name_of_university) %>% 
  dplyr::count(name_of_university) %>% 
  dplyr::arrange(desc(n)) %>% 
  dplyr::slice_head(n = 10) -> number_2_data


####make sure you call the data so it will display in your report

number_2_data %>% 
  dplyr::slice(n = -1) %>% 
  ggplot2::ggplot(mapping = aes(y = reorder(name_of_university, n), x = n)) +
  ggplot2::geom_bar(stat = "identity",
                    mapping = aes(fill = name_of_university),
                    show.legend = FALSE) +
  ggplot2::theme_minimal() +
  ggplot2::labs(x = "Number of Nobel Prize", 
                y = "Name of University") +
  ggplot2::geom_text(mapping = aes(label = n), hjust = "outward") -> number_2_fig


number_2_fig



```

## Part 3

Using words, describe the *third* visualization you are going to make using which variables/characteristics in your data:

*3. Box plot: average age of winners by category.*

```{r data_3}
nobel %>% 
  dplyr::select(gender, age, category) %>% 
  dplyr::group_by(category) %>% 
  dplyr::summarise(mean = mean(age)) %>% 
  dplyr::mutate(mean = round(mean, 0)) -> number_3_data


number_3_data %>% 
  ggplot2::ggplot(mapping = aes(x = category, y = mean, fill = category)) +
  ggplot2::geom_bar(stat = "identity") +
  ggplot2::coord_polar() +
  ggplot2::geom_text(mapping = aes(label = paste0(category, " - ", mean))) +
  ggplot2::scale_y_continuous(labels = scales::number) +
  ggplot2::theme_void() +
  ggplot2::theme(legend.position = "none")+
  ggplot2::labs(title = "Average age of Winners by Category") -> number_3_fig


number_3_fig

```


# last fig, order from largest to smallest next time
# submit