---
  title: "Data Review"
author: "SLEE"
date: "10/14/2022"
output: html_document
---

```{r setup, include=FALSE}

#####Make sure you load any required packages.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
library(openxlsx)
library(readxl)
library(writexl)
library(reshape2)
library(skimr)
library(janitor)
library(lubridate)
library(ggthemes)


```

## Import Your Data

In the following code hunk, import your data.

```{r data_import}

#### Use read_csv() or another function
#### Make sure your data is converted into a tibble. 


nobel <- read.csv("nobel_final.csv")

nobel %>% 
  tibble::as.tibble() -> nobel

nobel

```

## Part 1

Using words, describe the visualization you are going to make using which variables/characteristics in your data:

*1. Histograms and density plots: distributions of winners by age.*

In the code chunk below, show your work filtering the data and create the subset of data you will display graphically.

```{r data_1}
nobel %>% 
  dplyr::select(age_get_prize) -> number_1_data


####make sure you call the data so it will display in your report

winners_by_age %>% 
    ggplot2::ggplot(mapping = aes(x = age_get_prize)) +
  ggplot2::geom_histogram() -> number_1_fig


```

## Part 2

Using words, describe the *second* visualization you are going to make using which variables/characteristics in your data:

*2. Bar charts: winners by Top 10 university*

In the code chunk below, show your work filtering the data and create the subset of data you will display graphically.

```{r data_2}
nobel %>% 
  dplyr::select(name_of_university) %>% 
  dplyr::count(name_of_university) %>% 
  dplyr::arrange(desc(n)) %>% 
  dplyr::slice_head(n = 10) -> number_2_data


####make sure you call the data so it will display in your report

number_2_data %>% 
  ggplot2::ggplot(mapping = aes(y = reorder(name_of_university, n), x = n)) +
  ggplot2::geom_bar(stat = "identity",
                    mapping = aes(fill = name_of_university),
                    show.legend = FALSE) +
  ggplot2::theme_minimal()

# You still need to delete first one.. that's total
# x and y axis name
# label

```

## Part 3

Using words, describe the *third* visualization you are going to make using which variables/characteristics in your data:

*3. Box plot: average age of winners by gender, average age of winners by category.*

```{r data_3}
fig_dat3<-dat %>% filter(cyl==6) %>% select(qsec) 
####make sure you call the data so it will display in your report
fig_dat3
```
